Approximation as Differentiation

### 2025-06-09 main/first-order.tex
CMon.

For differentiable functions, we can combine linear approximations by adding tangent vectors. For stable
functions, we can combine approximants by taking their meet. The additive structure in both cases form a
commutative monoid with an addition + and zero element 0. A category $\cat{C}$ is enriched in $\CMon$, the
category of commutative monoids, if every hom-set $\cat{C}(X,Y)$ has a similar additive structure, providing
an operation + to add morphisms together plus a zero morphism $0: X \to Y$, and if composition is
\emph{bilinear}, i.e.~given by a family of morphisms $\Hom{\cat{C}}{Y}{Z} \tensor \Hom{\cat{C}}{X}{Y} \to
\Hom{\cat{C}}{X}{Z}$ in $\CMon$ that preserve the additive structure in $\Hom{\cat{C}}{Y}{Z}$ and
$\Hom{\cat{C}}{X}{Y}$ separately:

>>>>

For differentiable functions, we can combine linear approximations by adding tangent vectors. For stable
functions, we can combine approximants by taking their meet. The additive structure in both cases form a
commutative monoid with an addition + and zero element 0. A category $\cat{C}$ is enriched in $\CMon$ (or a
$\CMon$-category), the category of commutative monoids, if every hom-set $\cat{C}(X,Y)$ has a similar additive
structure, providing an operation + to add morphisms together plus a zero morphism $0: X \to Y$, and if
composition is \emph{bilinear}, i.e.~given by a family of morphisms $\Hom{\cat{C}}{Y}{Z} \tensor
\Hom{\cat{C}}{X}{Y} \to \Hom{\cat{C}}{X}{Z}$ in $\CMon$ that preserve the additive structure in
$\Hom{\cat{C}}{Y}{Z}$ and $\Hom{\cat{C}}{X}{Y}$ separately:
